---
title             : "@@title@@"
shorttitle        : "@@shorttitle@@"

author: 
  - name          : "@@author@@"
    affiliation   : "1*"
    corresponding : yes    # Define only one corresponding author
    address       : "@@inst@@" 
    email         : "@@email@@"


affiliation:
  - id            : "1"
    institution   : "@@inst@@"

abstract: |
  This is the abstract.
 
keywords          : "@@keywords@@" 

bibliography      : ["@@bibliography@@.bib"]
bibliostyle       : apa-5th-edition.csl

fontsize          : 9pt
figsintext        : yes
fig_caption				: true
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no

class             : "jou"
output            : papaja::apa6_pdf
---
	
```{r global_options, include = FALSE}
# set global options for output images
# tidy.opts = margin cutoff point and wraps text to the next line
knitr::opts_chunk$set(fig.path = "../output/Figures/", 
                      echo = FALSE, warning = FALSE, message = FALSE,
                      tidy.opts = list(width.cutoff = 72))

# set global options for knitr
knitr::opts_knit$set(progress = TRUE, verbose = TRUE)

```
```{r load_packages, include = FALSE, warning = FALSE, message = FALSE}

# for knitting latex to pdf in windows
Sys.setenv(JAVA_HOME = "C:\\Programme\\Java\\jre1.8.0_171")

# filenames for figures
fig1 <- "../output/Figures/response_fig1.pdf"
fig2 <- "../output/Figures/response_fig2.pdf"
fig3 <- "../output/Figures/response_fig3.pdf"
fig4 <- "../output/Figures/response_fig4.pdf"
fig5 <- "../output/Figures/response_fig5.pdf"
fig6 <- "../output/Figures/response_fig6.pdf"

# load all variables and run analysis
source("response_do.R")

```
# Introduction

## Subsection 

```{r fig1capt}

fig1capt <- "**This is a figure caption.**"

```

```{r fig1, include = TRUE, fig.cap = fig1capt}

# plot data
#plot(p1)
# include_graphics(fig1)
```

# Methods

## Statistical analysis

## Data and code availability
This paper has been written using RStudio (Version 1.1.456) and knitr
(Version 1.20). All data and code are freely available online to ensure
reproducibility at @@github@@.

# Results

# Discussion

## Limitations

## Conclusions

# Acknowledgments

# Conflict of interest

# References

```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
